Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-14 article.tex
Use comments instead of iffalse

If presentation of TMHs on MHC-I would bring an evolutionary advantage 
in the recognition of pathogens by the immune system, 
it would follow that this is equally important for MHC-II, 
especially as CD4+ T cell help is needed for a long lasting CD8+Tcell 
response \cite{novy2007cd4}.

@@

\iffalse
	Transmembrane helices and strong MHC-II-binding peptides
	were predicted for a tuberculosis reference proteome 
	from \url{https://www.ebi.ac.uk/reference_proteomes}
	using the \verb;epitopeome; R package (\cite{epitopeome}).
	We picked the three MHC-II alleles that are most abundant 
	in the current human population, 
	which are DRB4*0101, HLA-DPA10103-DPB10402 
	\richel{
	  We decided for DPB1*0402, but there are multiple alleles matching.
	  I just picked the first one of the alleles matching, which are:
	  HLA-DPA10x-DPB10402, where x equals 103-110, 201-204, 301-303 or 401
	}
	and DQA1*0501/DQB1*0301 \richel{reference here}
	\frans{
	  Neem aan dat dit die ref is naar dat stukje van most common haplotype in human population. Misschien moeten we even de coverage erbij melden. 
	  Greenbaum, Jason, et al. "Functional classification of class II human leukocyte antigen (HLA) molecules reveals seven different supertypes and a surprising degree of repertoire sharing across supertypes." Immunogenetics 63.6 (2011): 325-335.
	}.
	The 5\% peptides with the lowest IC50 values were defined as binders.
	We then simply counted the number of amino acids that were present inside the
	cell, within the membrane or outside of the cell, as well as if it was part 
	of a strong MHC-II binding site, as shown in figure \ref{tab:results}.

	The \verb;epitopeome; R package (\cite{epitopeome}) binds 
	together the \verb;tmhmm; (\cite{tmhmm}) and \verb;netmhc2pan; 
	(\cite{netmhc2pan}) 
	R packages. \verb;tmhmm; provides an R interface to
	TMHMM (\cite{krogh2001predicting, sonnhammer1998hidden}), a tool
	to predict where membrane proteins' amino acids are located within the
	membrane.   
	\verb;netmhc2pan; provides an R interface to
	NetMHC2pan (\cite{jensen2018improved}), a tool
	to predict MHC-II binding to proteins.
\fi

@@

\iffalse

	\frans{
	  Ik heb zitten denken over de evolutie naast conservering is occurrence ook heel belangrijk. Moeten we de mate van conservering niet wegen ten opzichte van de occurrence.
	  Wat ik daarmee bedoel is data als je kiest voor een mega geconseveerd epitope maar van dat type komen er maar 40 in een proteome voor versus een minder geconserveerd epitope maar daar zijn wel 100.000 varianten van dan heb je meer kans om 1 van die 100.000 te pakken toch? 
	}
	The evolutionary conservation of TMHs was measured from a
	DNA alignment of multiple transmembrane proteins in multiple
	species of the mycoplasma bacterial family
	\richel{how obtained exactly? how alignment done?}
	\frans{
	Via entrez en blast 
	  Ik he been transcript van Maxim ik zal dit proberen te vertalen naar een stukje tekst. 
	}
	.
	Using the \verb;tmhprot; R package (\cite{tmhprot}), the DNA alignment is split
	into two alignments, one for the TMH parts, another for the non-TMH
	parts. Each alignment was tested by the \verb;mcbette; 
	R package (\cite{mcbette}) to select the Bayesian inference model with
	the highest evidence (a.k.a. the marginal likelihood) using the nested
	sampling approach as described in \cite{maturana2018model},
	using the popular Bayesian phylogenetic tool 
	BEAST2 (\cite{bouckaert2014beast}) in the back-end.
	\verb;mcbette; used a set of 40 candidate inference models, 
	consisting of all combinations of 
	4 site models (JC, HKY, TN, GTR), 
	2 clock models (strict, RLN) and 
	5 tree priors (Yule, BD, CBS, CCP, CEP).

	For each alignment, the inference model with the highest evidence
	is used in a Bayesian inference. From each Bayesian posterior,
	the parameter estimates regarding mutation rates (including clock rate)
	were obtained and compared to determine which realized mutation rate is lower.
	The Markov chain Monte Carlo was set up in such a way that the effective sample
	size for the likelihood of the inference model is above the recommended value
	of 200 (\cite{bouckaert2014beast}).
\fi

@@

\iffalse
	Table \ref{tab:results} shows the location and binding strength for the
	tuberculosis proteome.

	\begin{figure}[ht]
	  \includegraphics[width=\textwidth]{figure_1.png}
	  \label{fig:1}
	\end{figure}

	\begin{figure}[ht]
	  \includegraphics[width=\textwidth]{figure_1_5.png}
	  \label{fig:1_5}
	\end{figure}

	\begin{figure}[ht]
	  \includegraphics[width=\textwidth]{figure_3.png}
	  \label{fig:3}
	\end{figure}

	\input{table_imoimo.latex}
	% has label tab:results
	\richel{
	  I'd enjoy 
	  (1) a row with 'expected by chance', 
	  (2) using percentages instead,
	  (3) merging inside and outside
	}

	The inference model with the highest evidence in the
	TMH-only alignment was [yet unknown] and [also yet unknown]
	for the non-TMH alignment. Individual model weights are shown
	in tables \ref{tab:evidences_tmh} 
	and \ref{tab:evidences_non_tmh}.

	The Bayesian inference resulted in [a distribution of mutation rates],
	as shown in [absent figure].
	The ESSes of the Bayesian parameter estimates was above 200, exact values
	are shown in tables \ref{tab:esses_tmh} and \ref{tab:esses_non_tmh}.
\fi

@@

\iffalse
	We conclude that MHC-II binds to TMH peptides with a higher/lower/equal
	probability than expected by chance.

	We conclude that the evolutionary conservation if the TMH parts of membrane
	proteins is higher/less/equal compare to its non-TMH counterparts.
\fi

@@

\iffalse
	\frans{
	  De TMH evolutie data van COVID is missachien interresanter. Ik zie het als volgt. 
	  COVID is een mooi voorbeeld van een virus 
	  Myco van een bacterie
	  In de bacterie is duidelijk dat tenmisnte voor MHCII TMHs zijn overgrepresenteerd virus niet. 
	  Dus verhaal kan zijn dat TMHs belangrijk voot bacteirele afweer niet zozeer voor virussen.

	  Hiervoor moeten we MHC-I doen voor myco
	  Kijken wat evolutie data doet voor virus dan evt kijken wat dit doet voor myco en vergelijken. 
	}

	We compared the mutation rates between the TMH and non-TMH part of
	multiple mycoplasma species. Where we expect no variation 
	in mutation rate for every TMH amino acid,
	\richel{
	  we can test this, but unsure if that would make sense
	}
	we know that non-TMH part will have regions of different evolutionary
	conservation: functional domains, especially in protein-protein
	interactions will be strongly conserved, due to an even more constrained
	set of peptides that enable a certain function.

	\richel{
	  Note that most bacteria are opportunistic pathogens.
	  Note that most bacteria are generalists.
	  Note that most bacteria have different cell membranes (and walls), that
	  may have different functional constraints than a human cell membrane
	}
\fi

>>>>

If presentation of TMHs on MHC-I would bring an evolutionary advantage 
in the recognition of pathogens by the immune system, 
it would follow that this is equally important for MHC-II, 
especially as CD4+ T cell help is needed for a long lasting CD8+ T cell 
response \cite{novy2007cd4}.

@@

	% Transmembrane helices and strong MHC-II-binding peptides
	% were predicted for a tuberculosis reference proteome 
	% from \url{https://www.ebi.ac.uk/reference_proteomes}
	% using the \verb;epitopeome; R package (\cite{epitopeome}).
	% We picked the three MHC-II alleles that are most abundant 
	% in the current human population, 
	% which are DRB4*0101, HLA-DPA10103-DPB10402 
	% \richel{
	%   We decided for DPB1*0402, but there are multiple alleles matching.
	%   I just picked the first one of the alleles matching, which are:
	%   HLA-DPA10x-DPB10402, where x equals 103-110, 201-204, 301-303 or 401
	% }
	% and DQA1*0501/DQB1*0301 \richel{reference here}
	% \frans{
	%   Neem aan dat dit die ref is naar dat stukje van most common haplotype in human population. Misschien moeten we even de coverage erbij melden. 
	%   Greenbaum, Jason, et al. "Functional classification of class II human leukocyte antigen (HLA) molecules reveals seven different supertypes and a surprising degree of repertoire sharing across supertypes." Immunogenetics 63.6 (2011): 325-335.
	% }.
	% The 5\% peptides with the lowest IC50 values were defined as binders.
	% We then simply counted the number of amino acids that were present inside the
	% cell, within the membrane or outside of the cell, as well as if it was part 
	% of a strong MHC-II binding site, as shown in figure \ref{tab:results}.

	% The \verb;epitopeome; R package (\cite{epitopeome}) binds 
	% together the \verb;tmhmm; (\cite{tmhmm}) and \verb;netmhc2pan; 
	% (\cite{netmhc2pan}) 
	% R packages. \verb;tmhmm; provides an R interface to
	% TMHMM (\cite{krogh2001predicting, sonnhammer1998hidden}), a tool
	% to predict where membrane proteins' amino acids are located within the
	% membrane.   
	% \verb;netmhc2pan; provides an R interface to
	% NetMHC2pan (\cite{jensen2018improved}), a tool
	% to predict MHC-II binding to proteins.

@@

	% \frans{
	%   Ik heb zitten denken over de evolutie naast conservering is occurrence ook heel belangrijk. Moeten we de mate van conservering niet wegen ten opzichte van de occurrence.
	%   Wat ik daarmee bedoel is data als je kiest voor een mega geconseveerd epitope maar van dat type komen er maar 40 in een proteome voor versus een minder geconserveerd epitope maar daar zijn wel 100.000 varianten van dan heb je meer kans om 1 van die 100.000 te pakken toch? 
	% }
	% The evolutionary conservation of TMHs was measured from a
	% DNA alignment of multiple transmembrane proteins in multiple
	% species of the mycoplasma bacterial family
	% \richel{how obtained exactly? how alignment done?}
	% \frans{
	% Via entrez en blast 
	%   Ik he been transcript van Maxim ik zal dit proberen te vertalen naar een stukje tekst. 
	% }
	% .
	% Using the \verb;tmhprot; R package (\cite{tmhprot}), the DNA alignment is split
	% into two alignments, one for the TMH parts, another for the non-TMH
	% parts. Each alignment was tested by the \verb;mcbette; 
	% R package (\cite{mcbette}) to select the Bayesian inference model with
	% the highest evidence (a.k.a. the marginal likelihood) using the nested
	% sampling approach as described in \cite{maturana2018model},
	% using the popular Bayesian phylogenetic tool 
	% BEAST2 (\cite{bouckaert2014beast}) in the back-end.
	% \verb;mcbette; used a set of 40 candidate inference models, 
	% consisting of all combinations of 
	% 4 site models (JC, HKY, TN, GTR), 
	% 2 clock models (strict, RLN) and 
	% 5 tree priors (Yule, BD, CBS, CCP, CEP).

	% For each alignment, the inference model with the highest evidence
	% is used in a Bayesian inference. From each Bayesian posterior,
	% the parameter estimates regarding mutation rates (including clock rate)
	% were obtained and compared to determine which realized mutation rate is lower.
	% The Markov chain Monte Carlo was set up in such a way that the effective sample
	% size for the likelihood of the inference model is above the recommended value
	% of 200 (\cite{bouckaert2014beast}).

@@

	% Table \ref{tab:results} shows the location and binding strength for the
	% tuberculosis proteome.

	% \begin{figure}[ht]
	%   \includegraphics[width=\textwidth]{figure_1.png}
	%   \label{fig:1}
	% \end{figure}

	% \begin{figure}[ht]
	%   \includegraphics[width=\textwidth]{figure_1_5.png}
	%   \label{fig:1_5}
	% \end{figure}

	% \begin{figure}[ht]
	%   \includegraphics[width=\textwidth]{figure_3.png}
	%   \label{fig:3}
	% \end{figure}

	% \input{table_imoimo.latex}
	% % has label tab:results
	% \richel{
	%   I'd enjoy 
	%   (1) a row with 'expected by chance', 
	%   (2) using percentages instead,
	%   (3) merging inside and outside
	% }

	% The inference model with the highest evidence in the
	% TMH-only alignment was [yet unknown] and [also yet unknown]
	% for the non-TMH alignment. Individual model weights are shown
	% in tables \ref{tab:evidences_tmh} 
	% and \ref{tab:evidences_non_tmh}.

	% The Bayesian inference resulted in [a distribution of mutation rates],
	% as shown in [absent figure].
	% The ESSes of the Bayesian parameter estimates was above 200, exact values
	% are shown in tables \ref{tab:esses_tmh} and \ref{tab:esses_non_tmh}.

@@

	% We conclude that MHC-II binds to TMH peptides with a higher/lower/equal
	% probability than expected by chance.

	% We conclude that the evolutionary conservation if the TMH parts of membrane
	% proteins is higher/less/equal compare to its non-TMH counterparts.

@@

	% \frans{
	%   De TMH evolutie data van COVID is missachien interresanter. Ik zie het als volgt. 
	%   COVID is een mooi voorbeeld van een virus 
	%   Myco van een bacterie
	%   In de bacterie is duidelijk dat tenmisnte voor MHCII TMHs zijn overgrepresenteerd virus niet. 
	%   Dus verhaal kan zijn dat TMHs belangrijk voot bacteirele afweer niet zozeer voor virussen. 
	% 
	%   Hiervoor moeten we MHC-I doen voor myco
	%   Kijken wat evolutie data doet voor virus dan evt kijken wat dit doet voor myco en vergelijken. 
	% }
	% 
	% We compared the mutation rates between the TMH and non-TMH part of
	% multiple mycoplasma species. Where we expect no variation 
	% in mutation rate for every TMH amino acid,
	% \richel{
	%   we can test this, but unsure if that would make sense
	% }
	% we know that non-TMH part will have regions of different evolutionary
	% conservation: functional domains, especially in protein-protein
	% interactions will be strongly conserved, due to an even more constrained
	% set of peptides that enable a certain function.

	% \richel{
	%   Note that most bacteria are opportunistic pathogens.
	%   Note that most bacteria are generalists.
	%   Note that most bacteria have different cell membranes (and walls), that
	%   may have different functional constraints than a human cell membrane
	% }
